Data-driven Reduction of Multiscale Stochastic Dynamical Systems

### 2014-07-17 reducible_SDE/paper/paper_draft.tex
edited paper'

@@

Error and estimation analysis of NIVs (remark that applies to more general settings): give conditions/bounds when we can recover the intrinsic slow variable

Empirical configuration/demonstration of the method, how to use the analysis to set the parameters in the algorithm

@@

 Define the following two-dimensional system of SDEs
\begin{eqnarray}
dX(1) &=& 3 dt + dW_1 \\ 
dX(2) &=& \frac{-X(2)}{\epsilon} dt + dW_2 
\end{eqnarray}
where $W_1, W_2$ are independent Brownian motions, and $\epsilon \ll 1$.

Let
\begin{eqnarray}
f^1(X) &=& X(1) + \frac{ X(2)^2}{\epsilon} \\
f^2(X) &=& \frac{X(2)}{\sqrt{\epsilon}}
\end{eqnarray}
Therefore, $X(2)$ is now a ``fast'' variable, and we have further applied a nonlinear transformation to this fast-slow system.

@@

@@

@@

>>>>

\usepackage{subcaption}

@@

\begin{itemize}
\item Error and estimation analysis of NIVs (remark that applies to more general settings): give conditions/bounds when we can recover the intrinsic slow variable
%
\item Empirical configuration/demonstration of the method, how to use the analysis to set the parameters in the algorithm
\end{itemize}

@@

 Define the following two-dimensional system of SDEs
\begin{eqnarray} \label{eq:init_data}
dX(1) &=& 3 dt + dW_1 \\ 
dX(2) &=& \frac{-X(2)}{\epsilon} dt + dW_2 
\end{eqnarray}
where $W_1, W_2$ are independent Brownian motions, and $\epsilon \ll 1$.

Let
\begin{eqnarray}\label{eq:transformed_data}
f^1(X) &=& X(1) + \frac{ X(2)^2}{\epsilon} \\
f^2(X) &=& \frac{X(2)}{\sqrt{\epsilon}}
\end{eqnarray}
Therefore, $X(2)$ is now a ``fast'' variable, and we have further applied a nonlinear transformation to this fast-slow system.

@@

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{data_init}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{data_transformed}
\caption{}
\end{subfigure}
\caption{(a) The original data, simulated from \eqref{eq:init_data}. (b) The data from (a), transformed according to \eqref{eq:transformed_data}. }
\label{fig:initial_data}
\end{figure}

@@

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{data_transformed_colored_NIV}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{data_transformed_colored_DMAPS}
\caption{}
\end{subfigure}
\caption{(a) The data from Figure~\ref{fig:initial_data}(b), colored by the first NIV. Note that we recover the slow variable. (b) The data from Figure~\ref{fig:initial_data}(b), colored by the first DMAPS variable. Note that we do {\em not} recover the slow variable.  }
\label{fig:NIV_versus_DMAPS}
\end{figure}

@@

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{errors_function_dt}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{empirical_totaldist_function_dt}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{errors_function_dy}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{empirical_totaldist_function_dy}
\caption{}
\end{subfigure}
\caption{(a) Analytical estimation of errors as a function of $\delta t$. 
%
(b) Empirical estimation of total distance as a function of $\delta t$.  
%
(c) Analytical estimation of errors as a function of $\Delta Y$. 
%
(d) Empirical estimation of total distance as a function of $\Delta Y$}
\end{figure}
